Report

### 2024-09-11 tutorial.Rmd
fix reproducibility 1

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
library(targets)
tar_load_everything()
```

@@

```{r echo = FALSE, eval = TRUE}
out <- capture.output(print(res_rma, digits = 2))
out <- out[c(2:4, 8:15)]
out <- out[!out == ""]
cat(out, sep = "\n")
```

@@

```{r echo = TRUE, eval = FALSE}
set.seed(1)
pbf(yi = kuiper2013$beta,
    vi = kuiper2013$vi,
    ni = kuiper2013$n,
    hypothesis = "y = 0; y > 0; y < 0")
```
```{r echo = FALSE, eval = TRUE}
print_pbf <- function(x){
  out <- x
  out[,] <- sapply(x, formatC, digits = 2, format = "f")
  if(any(nchar(unlist(out)) > 8)){
    for(i in 1:nrow(out)){
      for(j in 1:ncol(out)){
        if(nchar(out[i,j]) > 8){
          out[i,j] <- formatC(x[i,j], format = "e", digits = 2)
        }
      }
    }
  }
  print(out)
}
print_pbf(res_pbf_t1)
```

@@

}
print_bain(res_t2, digits = 2)
```

@@

# Bind the models into a list
results <- list(results_nl, results_dk, results_us)
# Test the hypothesis that the effect size labeled 'beta' is positive
set.seed(1)
pbf(results, hypothesis = "beta > .1", standardize = TRUE)
```
```{r, eval = TRUE, echo = FALSE}
print_pbf(res_pbf_t3)
```

@@

```{r, echo = FALSE, eval = TRUE}
print_pbf(res_pbf4)
```

@@

```{r echo = FALSE, eval = TRUE}
print_pbf(res_pbf_t5)
```

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
library(targets)
```

@@

```{r echo = FALSE, eval = TRUE}
tar_load("res_rma")
out <- capture.output(print(res_rma, digits = 2))
out <- out[c(2:4, 8:15)]
out <- out[!out == ""]
cat(out, sep = "\n")
```

@@

```{r echo = TRUE, eval = FALSE}
set.seed(1)
pbf(yi = kuiper2013$beta,
    vi = kuiper2013$vi,
    ni = kuiper2013$n,
    hypothesis = "y = 0; y > 0; y < 0")
```
```{r echo = FALSE, eval = TRUE}
print_pbf <- function(x){
  out <- x
  out[,] <- sapply(x, formatC, digits = 2, format = "f")
  if(any(nchar(unlist(out)) > 8)){
    for(i in 1:nrow(out)){
      for(j in 1:ncol(out)){
        if(nchar(out[i,j]) > 8){
          out[i,j] <- formatC(x[i,j], format = "e", digits = 2)
        }
      }
    }
  }
  print(out)
}
tar_load("res_pbf_t1")
print_pbf(res_pbf_t1)
```

@@

}
tar_load("res_t2")
print_bain(res_t2, digits = 2)
```

@@

# Bind the models into a list
results <- list(results_nl, results_dk, results_us)
# Test the hypothesis that the effect size labeled 'beta' is positive
set.seed(1)
pbf(results, hypothesis = "beta > .1", standardize = TRUE)
```
```{r, eval = TRUE, echo = FALSE}
tar_load("res_pbf_t3")
print_pbf(res_pbf_t3)
```

@@

```{r, echo = FALSE, eval = TRUE}
tar_load("res_pbf4")
print_pbf(res_pbf4)
```

@@

```{r echo = FALSE, eval = TRUE}
tar_load("res_pbf_t5")
print_pbf(res_pbf_t5)
```
